---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# safeinstall

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/Pakillo/safeinstall.svg?branch=master)](https://travis-ci.org/Pakillo/safeinstall)
[![Codecov test coverage](https://codecov.io/gh/Pakillo/safeinstall/branch/master/graph/badge.svg)](https://codecov.io/gh/Pakillo/safeinstall?branch=master)
<!-- badges: end -->

The goal of `safeinstall` is to run some basic security checks before installing an R package from an online repository (like GitHub). This package is basically a wrapper of [defender](https://github.com/ropenscilabs/defender) so that some security checks are done before running `remotes::install_github`. 

## Installation

``` r
remotes::install_github("Pakillo/safeinstall")
```

## Usage

```{r}
library(safeinstall)
```

`safe_install_github` is like `remotes::install_github` but will run some checks before installing the package. If nothing wrong is detected, the package is installed.

```{r eval=FALSE}
safe_install_github("Pakillo/safeinstall")
```

In contrast, if potentially unsafe code is detected (e.g. system calls), the package will not install and an error will be returned.

```{r eval=TRUE, error=TRUE}
safe_install_github("ropenscilabs/testevil")
```


### Checking any git repository

To just scan a package (without installing), run `check_package` on the git repository:

```{r}
check_package("https://github.com/Pakillo/safeinstall.git")
```

Will return TRUE if no problem is found, or FALSE (plus info on potential problems) otherwise:

```{r}
check_package("https://github.com/ropenscilabs/testevil.git")
```

This works with any git repository (not only GitHub), e.g. on Gitlab:

```{r}
check_package("https://gitlab.com/jimhester/covr.git")
```

