---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# safeinstall

<!-- badges: start -->
<!-- badges: end -->

The goal of safeinstall is to run some basic security checks before installing an R package from an online repository (like GitHub). This package is basically a wrapper of [defender](https://github.com/ropenscilabs/defender) that runs some checks before running `remotes::install_github`. 

## Installation

``` r
devtools::install_github("Pakillo/safeinstall")
```

## Usage

`safe_install_github` will run some checks before installing the package. If nothing is detected, the package is installed.

```{r eval=FALSE}
library(safeinstall)

safe_install_github("Pakillo/safeinstall")
```

In contrast, the package will not install if malicious/unsafe code is potentially detected.

```{r eval=FALSE}
safe_install_github("ropenscilabs/testevil")
```

